% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file. 

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig}
\usepackage{color}

\usepackage{graphicx, subfigure}
\usepackage{url}

\def\todo#1{{\bf \textcolor{red}{TODO:~#1}}}
\def\question#1{{\bf \textcolor{purple}{Question:~#1}}}
\def\comment#1{{\bf \textcolor{blue}{~#1}}}
\def\etal{et\ al.\ }

\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf TrustFA: TrustZone-Assisted Facial Authentication on Smartphone}

%for single author (just remove % characters)
\author{
{\rm Dongli Zhang}\\
Stony Brook University
\and
{\rm Radu Sion}\\
Stony Brook University
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}


\subsection*{Abstract}

Nowadays, many applications, such as Facebook, Dropbox and mobile banking,
allow users to login and use the remote services via smartphones. Because of
the limitations of credential-based authentication, biometric authentication is
becoming popular. Facial authentication is one of the popular biometric
authentication techniques and it consists of three phases: first, the photo is
captured by hardware camera; second, the smartphone application retrieves the
photo from hardware camera via OS; third, the smartphone application
authenticates the user by sending the photo (or its extracted features) to
remote services.  To achieve the trusted facial authentication, all three
phases should be secured.  In this paper, we propose TrustFA, a
TrustZone-assisted solution to secure all three phases in facial authentication
on smartphone.  We leverage the ARM TrustZone technique to capture the photo
and collect the accelerometer data in TrustZone secure world.  As all of the
secure world memory, peripherals and interrupts are isolated from normal world
legacy OS, attackers even with root privilege in legacy OS would not be able to
break the authentication. Within our knowledge, this is the first effort that
all of three phases in facial authentication are secured. Compared to prior
works, the threat model regarding smartphone facial authentication assumed in
this paper is the most strongest.  Since the prototyping is still in progress,
we envision the implementation of TrustFA on Freescale i.MX53 Quick Start Board
(QSB).


%However, 2D facial authentication still has two issues. First, 2D media attack
%makes the 2D facial authentication untrusted. The attacker could just put a
%photo in front of the camera to cheat the authentication program.  Second, the
%large TCB of legacy OS makes the smartphone vulnerable to malwares.  The
%untrusted legacy OS would tamper the photo/video captured by the camera (e.g.,
%virtual camera attack). 

\input{introduction}
\input{design}
\input{implementation}
\input{discussion}
\input{related}
\input{conclusion}

{\footnotesize \bibliographystyle{acm}
\bibliography{refs}}


%\theendnotes

\end{document}







